\documentclass[12pt,a4paper]{report}
\usepackage{enumerate} 
\usepackage{amsfonts}
\usepackage{amssymb} %% gothic letters with \mathfrak{}
\usepackage{hyperref} % hiperlinks
\usepackage{color} % colors
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% spoiler alert!!!
{\Huge\textbf{\color{red}
SPOILER ALERT!!! \\[1cm]
ALL INFO IN THIS FILE ARE SPOILERS!!!
}}
%%%%%

\section{Names for characters, places and items}
TODO

Names that we need to chose:
\begin{itemize}
\item Hero: \textbf{Eldran}
\item Princess: \textbf{Robyne (?)}
\item Main villain:
\item Secondary villains:
\item Country and region:
\item Witch, blacksmith, boss of the town,...:
\item Some item names (???):
\item Names for places:
\item World(planet):
\item Binary star (2 names): Lux and Umbra (?)
\end{itemize}

%%%%%%%%%%%%%%
\section{Brainstorming for the background story}

Intro story (we could add static images):

{\it
Ancient legends tell of distant binary star, where the planet ??? swung.  \\

This planet was inhabited by magical creatures of light and darkness that coexisted in harmony. \\

But one day, a small meteor coming from the star fell to the planet surface. \\

After the impact, a divine artefact with medallion shape was found in the crater. \\

The wisest of the light creatures studied the artefact and discovered a limitless mystic power sealed inside.
Its power held the answers for the meaning of all existence. \\

The medallion artefact was called the Solarus. \\

A wave of greed for the artefact sprout amongst the creatures of darkness.
And a war for the artefact began soon thereafter. \\

The creatures of light tried to use the power of the artefact to seal away the creatures of darkness and stop the war.
But something went wrong. \\

The artifact shattered, and the world was divided in two twin worlds: the worlds of light and darkness.
The pieces of the artefact were scattered in both worlds, and protected by light and dark creatures that became their guardians. \\

Most of the ancient creatures disappeared without leaving a trace, centuries of years before humans arrival to the light world.

According to ancient prophecies, the lords of darkness will someday find a way to the light world, in search of the pieces
of the Solarus artefact to gain the power to control the world.
} % End of italic format.

[Remark: there will be 8 elemental spirits, one of each element. These could be: wind, water, fire, moon, wood, light,
darkness/shadow, and earth; like in secret of mana, but we probably should change some of the elements to make them fit better
with the types of the dungeons. The guardians will be the final bosses of each dungeon, so these must be related to some element.]

[Remark: when the artifact was broken, the binary star, Lux-Umbra , was divided too. (Change the names if necessary!.)
The red star Lux was detached with the light world, and the blue start Umbra with the dark world.
Prophecies say that if the artefact is used to fuse both worlds together again, the two stars may collapse and the world will be destroyed.
More secret info about the background story will be found in some library, and there will be some secret books hidden in caves/houses.]


%%%%%%%%%%%%%%
\section{Brainstorming for the main story}

$\bullet$ \textbf{Before level 1:} ... \\
$\bullet$ \textbf{Inside level 1:} ... \\
... \\
$\bullet$ \textbf{Before level 5:} ... \\
$\bullet$ \textbf{Inside level 5:} In the castle dungeon the hero will die, but only apparently. He will be replaced by
the princess, that will be controled for a few levels (between 1 and 3 dungeons), and then we will have our main hero
back (that will be a surprise since the player will have thought that the hero is dead).

\indent In the final battle of the castle dungeon, or in a
battle cutscene before (it can be when you enter the back entrance at the beginning), the hero will find the princess under
attack of an enemy (the final boss of this level or some of the main villains); the enemy will throw a deadly attack
against the hero and a bloody explosion will hapen on the hero. If this happens in a battle, it can happen as the last attack
of the enemy at the moment he is dying (it would be like both the hero and enemy dying at the same time). The princess will be
present in the same room during the all battle (or cutscene battle).

\indent The items of the hero will fall to the ground with a bag item image and the princess will get close to it (in a cutscene);
a dialog appears, something like \textit{There is a pool of blood. You found Eldran's equipment}. Then the princess escapes from
the room and the the control is returned to the player. The princess wants to take revenge. She will finish the dungeon (or continue to the next one in case this happens in the boss battle of this dungeon.) The inventory will be the same.

\indent After a 1, 2 or 3 dungeons, a cutscene starts. Black screen and dialog, \textit{A few days before}; the battle cutscene is repeated
but in slow-motion, and you can see that the hero is teleported and replaced instantly by an animal. He then appears in a wizard's house,
teleported by magic, but he fall inconscious. A cutscene with wizards explains that the apprentice wizard was being trained by his master, he had used the wrong spell and used instead an interchanging teleportation spell that interchanged positions of the hero and the animal in
the last moment (the animal was killed in the bloody explosion instead of the hero). After the wizards conversation, they put the inconscious hero in some bed, and a dialog with black background is shown: \textit{Some days later}. The hero awakes, the wizards explain
what had happened and that they apologize for their mistake. You get the control of the hero, but the inventory is empty. Out of the house you discover that you are in the clouds (a small map). Other wizard of another house helps you to get back to the kingdom by teleportation.
There you find the princess, who gives you back your inventory, including the new items, and then Eldran is controlled again until the end of the game. Remark: to avoid problems of the game (like having different tunics for the heroes), it will be better to control the princess
only during the castle dungeon.

$\bullet$ \textbf{Before level 6:} ... \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}